<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-12-09 MainAnalysis.Rmd
Revised plotting function.

```{r, run_invivoPKfit_1comp}

@@

```{r, run_invivoPKfit_2comp}

@@

```{r, run_invivoPKfit_flat}
run_timestamp_flat <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

@@

```{r}
DF <- preprocess_data(data.set = cvt.data,
                       ratio.data.to.dose = 1,
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,)
```

```{r, read_data, eval = FALSE}
### this block reads the exported model fit csv files from run_invivoPKfit

pk_output_2comp <- read.csv(paste("inst/ext/PK_fit_table_2comp_",run_timestamp_1comp,".csv",sep=""))
pk_output_flat <- read.csv(paste("inst/ext/PK_fit_table_flat.",run_timestamp_2comp,".csv",sep=""))
pk_output_1comp <- read.csv(paste("inst/ext/PK_fit_table_1comp_",run_timestamp_flat,".csv",sep=""))

pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
```

Rowbind together all of the fitted parameter tables into one big one.
```{r}
pk_fit <- rbindlist(list("1comp" = PK.fit.table.1comp,
                         "2comp" = PK.fit.table.2comp,
                         "flat" = PK.fit.table.flat),
                    idcol = "Model",
                    use.names = TRUE,
                    fill = TRUE)
```

@@

```{r}
setorder(pk_fit,
         Analysis_Type,
         DTXSID,
         Species,
         AIC,
         na.last = TRUE)

pk_fit_win <- unique(pk_fit[, .(Analysis_Type, DTXSID, Species, model, AIC)] )
```

@@

```{r}

plot_table <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, Reference)])
plot_table <- plot_table[Analysis_Type %in% "Joint"]

tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
                     Analysis_Type_in = plot_table$Analysis_Type,
                     Reference_in = plot_table$Reference,
              MoreArgs = list(
                     model_in = c("1compartment", "2compartment", "flat"),
                     fitdata = DF,
                     pk_fit = pk_fit)
                     )
    ```

>>>>

```{r, run_invivoPKfit_1comp, eval = FALSE}

@@

```{r, run_invivoPKfit_2comp, eval = FALSE}

@@

Fit the flat model.

```{r, run_invivoPKfit_flat, eval = FALSE}
run_timestamp_flat <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

@@

```{r}
DF <- preprocess_data(data.set = cvt.data,
                       ratio.data.to.dose = 1,
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE)
```

```{r, read_data}
### this block reads the exported model fit csv files from run_invivoPKfit

PK.fit.table.1comp <- fread(paste0("inst/ext/", "PK_fit_table_1comp_2022_12_08_09_44_34.csv",sep=""))
PK.fit.table.2comp <- fread(paste0("inst/ext/", "PK_fit_table_2comp_2022_12_08_10_31_09.csv",sep=""))
PK.fit.table.flat <- fread(paste0("inst/ext/", "PK_fit_table_flat_2022_12_08_12_03_24.csv",sep=""))

#pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
```

Rowbind together all of the fitted parameter tables into one big one.
```{r}
pk_fit <- rbindlist(list("1comp" = PK.fit.table.1comp,
                         "2comp" = PK.fit.table.2comp,
                         "flat" = PK.fit.table.flat),
                    use.names = TRUE,
                    fill = TRUE)
```

@@

```{r}
tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, model, AIC)])
setorder(tmp, DTXSID, Species, Analysis_Type, AIC, na.last = TRUE)
model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type)]
pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type")]
pk_fit[, winning:=(model == winmodel)]

@@

Get unique combinations of DTXSID and species -- each of these will be one plot.

```{r}
plot_table <- unique(pk_fit[, .(DTXSID, Species)])
```

Plot all models for the joint analysis.
```{r}

#plot all models
tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
              MoreArgs = list(
                     model_in = "all",
                     Analysis_Type_in = "Joint",
                     DF = DF,
                     pk_fit = pk_fit,
                     n = 101,
                     log10_scale_time = FALSE,
                     file_path = "inst/ext/plots/Joint Analysis/model_all/")
                     )

Plot only the winning model

```{r}
#plot all models
tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
              MoreArgs = list(
                Analysis_Type_in = c("Joint", "Separate"),
                     model_in = "winning",
                     fitdata = DF,
                     pk_fit = pk_fit,
                     file_path = "inst/ext/plots/analysis_all_model_winning/",
                log10_scale_time = TRUE)
                     )
```
